Asymmetric relationships and their effects on coexistence

### 2023-02-01 paper/Paper.Rnw
continued progress editing Methods and accompanying SI sections (mostly working on the SI)

%Plotting shortcuts for the log-normal fecundities model
To explore, using the log-normal fecundities lottery model, the relative magnitudes of the contributions 
to coexistence that come from ATAs versus other mechanisms, we plotted the terms of the decomposition 
(\ref{eq:full_decomp}) for that model against the model parameters $\mu_1$, $\mu_2$, $\sigma$ and $\delta$.
We labeled regions of the plot which corresponded to ATA rescue or exclusion, i.e., regions for which
GWR and GWR-$\Delta_i^{[EC]}$ had opposite signs.
Some mathematical shortcuts, summarized here, simplified plotting. 
First, we assumed, without loss of generality, that $\mu_1 \leq \mu_2$. To understand coexistence, 
it was then sufficient to decompose GWR of the weaker competitor, species 1. 
Second, we showed that, for the log-normal fecundities
lottery model, none of the components of (\ref{eq:full_decomp}) depends independently on $\mu_1$ and $\mu_2$;
instead they depend only on $\mu_1-\mu_2$ (SI section \ref{SI-sect:math_simplifications}). 
%***DAN: Not sure if this will the right citation anymore after we restructure those parts of the SI
So we plotted against $\mu_1 - \mu_2$. 
Third, we showed that the values of all components in (\ref{eq:full_decomp}) were the same 
for both our left- and right-tail associated noises (SI section \ref{SI-sect:math_simplifications}). 
%***DAN: Also check this citation
So we only generated plots 
for left-tail associated noise. For each combination of $\delta=0.2, 0.4, 0.6$
and $\mu_1-\mu_2=0,-0.5,-2,-4$,
we plotted the components of (\ref{eq:full_decomp}) against $\sigma$. 
%***DAN: Jasmin mentioned that she only used \delta=0.2, .4, .6 because of a comment Ellner made where he 
%said it was known that larger values of \delta made for very little storage effects. Read that comment 
%again and then write something here to jstify the choice. I think I can probably then delete the section of
%sup mat, mentioned in the commented text below, that talks about \delta=1.
%Mathematical simplications for the $\delta=1$ case make it straightforward to see that
%coexistence is impossible and that the case is relatively trivial (SI 
%section \ref{SI-sect:delta1}), so that case is not plotted.  
The simulation methods of \cite{Ellner_2019} were used to compute the components of (\ref{eq:full_decomp}).
Computationally efficient means of performing these simulations are in 
SI section \ref{SI-sect:efficient_computation}.
%***DAN: check the citation after restructuring the SI

%Then a similar para for the beta-fecundity lottery model.
To explore, using the beta fecundities lottery model, the relative magnitudes of the contributions 
to coexistence that come from ATAs versus other mechanisms, we plotted the terms of the decomposition 
(\ref{eq:full_decomp}) for that model against the model parameters $\eta_1$, $\eta_2$, and $\delta$.
%***DAN: finish it

%For the sup mat, I think you will need these sections:
%S3 - on generating the Fig. 1 noise (only)
%S4 - as large section with subsections. About the theory for the two lottery models, but not about the effecient computation
%   Starts with material on the general lottery model
%   Then a sub-section with all the computations for the log-normal-fecundities lottery model
%   Then a sub-section for the beta-fecundities lottery model
%S5 - then a similar section, but for the efficient computations
%There might be additional sections, see the current sections and see if those need to be maintained
%as their own sections or can be absorbed into the above.
%This is going to take some work.

>>>>

%Plotting shortcuts for the log-normal fecundities model
To explore, using the log-normal fecundities lottery model, the relative magnitudes of the contributions 
to coexistence that come from ATAs versus other mechanisms, we plotted the terms of the decomposition 
(\ref{eq:full_decomp}) for that model against the model parameters $\mu_1$, $\mu_2$, $\sigma$ and $\delta$.
We labeled regions of the plot which corresponded to ATA rescue or exclusion, i.e., regions for which
GWR and GWR-$\Delta_i^{[EC]}$ had opposite signs.
Some mathematical shortcuts, summarized here, simplified plotting. 
First, we assumed, without loss of generality, that $\mu_1 \leq \mu_2$. To understand coexistence, 
it was then sufficient to decompose GWR of the weaker competitor, species 1. 
Second, we showed that, for the log-normal fecundities
lottery model, none of the components of (\ref{eq:full_decomp}) depends independently on $\mu_1$ and $\mu_2$;
instead they depend only on $\mu_1-\mu_2$ (SI section \ref{SI-SIsect:TheoryForLottery}). 
So we plotted against $\mu_1 - \mu_2$. 
Third, we showed that the values of all components in (\ref{eq:full_decomp}) were the same 
for both our left- and right-tail associated noises (SI section \ref{SI-SIsect:TheoryForLottery}). 
So we only generated plots 
for left-tail associated noise. For each combination of $\delta=0.2, 0.4, 0.6$
and $\mu_1-\mu_2=0,-0.5,-2,-4$,
we plotted the components of (\ref{eq:full_decomp}) against $\sigma$. 
%***DAN: Jasmin mentioned that she only used \delta=0.2, .4, .6 because of a comment Ellner made where he 
%said it was known that larger values of \delta made for very little storage effects. Read that comment 
%again and then write something here to jstify the choice. I think I can probably then delete the section of
%sup mat, mentioned in the commented text below, that talks about \delta=1.
%Mathematical simplications for the $\delta=1$ case make it straightforward to see that
%coexistence is impossible and that the case is relatively trivial (SI 
%section \ref{SI-sect:delta1}), so that case is not plotted.  
The simulation methods of \cite{Ellner_2019} were used to compute the components of (\ref{eq:full_decomp}).
Computationally efficient means of performing these simulations are in 
SI section \ref{SI-sect:efficient_computation}.

%Then a similar para for the beta-fecundity lottery model.
To explore, using the beta fecundities lottery model, the relative magnitudes of the contributions 
to coexistence that come from ATAs versus other mechanisms, we plotted the terms of the decomposition 
(\ref{eq:full_decomp}) for that model against the model parameters $\eta_1$, $\eta_2$, and $\delta$.
%***DAN: finish it
%***DAN: Next steps as of 2023 02 01:
%Fill in the sup mat section for the theory for the beta fecundities lottery model
%fill in the efficient computation section for that same model
%write this section, here, in the main text
